\textls[-0]{\thetitle}

### 2023-03-12 metatheory-condensed.tex
edit

For accessibility, we present MLTT using named variables and meta-level substitution,
however we emphasize that in the meta-theoretic reasoning carried out in the appendix, 
we will shift to debruijn indices and explicit substitution because it leads to clearer proof details.
We summarize the salient points before delving into the technical details for audience
unacquainted with MLTT.

>>>>

For accessibility of the main text, \cref{sec:metatheory2} presents \TT using
named variables and meta-level substitution.
For clarity of proof details, the technical appendix supplementing
\cref{sec:metatheory2} instead uses de Bruijn indices and explicit substitution.
%
We acknowledge that the presentation is dense for an audience
unacquainted with MLTT, so we summarize the salient points first.
